Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-18 nips_2018.tex
contributions

Prior work on program learning has largely assumed a fixed, hand-engineered DSL,
both in classic symbolic program learning approaches (e.g., Metagol:~\cite{muggleton2015meta},
FlashFill:~\cite{gulwani2011automating}),
neural approaches  (e.g., RobustFill:~\cite{devlin2017robustfill}), and hybrids of neural and
symbolic methods (e.g., Neural-guided deductive search:~\cite{ngds}, DeepCoder:~\cite{balog2016deepcoder}).
A notable exception is the EC algorithm~\cite{Dechter:2013:BLV:2540128.2540316},
which also learns a library of subroutines.
We were inspired by EC,
and go beyond it by giving a new algorithm that learns DSLs, as well as a way of combining DSL learning with
neurally guided program search.
In the experiments section,
we compared directly with EC,
showing empirical improvements.

The new contribution of this work is
thus an  algorithm for learning DSLs which jointly trains a neural net to
search for programs in the DSL.

@@

\begin{wraptable}{r}{0.6\textwidth}
%% This radically shrinks the table
\tabcolsep=4pt
\renewcommand{\arraystretch}{0.5}
\begin{tabular}{lllllll}
  \toprule& Ours& 
    No NN
& SE&NPS & PCFG & Enum

  %% \\\midrule\multicolumn{6}{c}{\emph{Boolean Circuits}}\\\midrule
  %% \% solved &
  %% \textbf{84\%} &76\%& 63\%&62\%&62\%\\
  %% Solve time&  0.9s&  1.1s&1.2s&1.3s&1.3s

  \\\midrule\multicolumn{7}{c}{\emph{List Processing}}\\\midrule
  \% solved&\textbf{79\%} &76\% &71\%&35\%&62\%&37\%\\
  Solve time&  4.1s&5.8s&10.6s&34.7s&43.4s&20.2s
  %NOTE: "Ours" result was without helmholtz

  \\\midrule\multicolumn{7}{c}{\emph{Text Editing}}\\\midrule
  \% solved&\textbf{74\%} &43\% &30\%&33\%&0\%&4\%\\
  Solve time&  29s&65s&38s&80s&--&235s

  %% \\\midrule\multicolumn{6}{c}{\emph{List functions (base DSL)}}\\\midrule
  %% \% solved&\textbf{52\%} &\textbf{52\%} &40\%&44\%&42\%\\
  %% Solve time&  0.4s&0.7s&1.2s&0.9s&1.0s

  \\\midrule\multicolumn{7}{c}{\emph{Symbolic Regression}}\\\midrule
  \% solved&   \textbf{84\% }&75\%&62\%&38\%&38\%&37\% \\
  Solve time&  \textbf{24}s& 40s  &28s&31s&55s&29s
  %% MDL (nats)&   9.3 &11.0&2.3&--&4.6

  \\\bottomrule
  \end{tabular}
\caption{\% solved before timeout. Solve time: averaged over solved
  tasks.  SE: NPS: trained like RobustFill/DeepCoder.  PCFG: model w/o
  structure learning.  Enum: model w/o any learning.  %% MDL:
  %% $-\expect\left[\probability[x|p] \right]$. For domains other than
  %% symbolic regression MDL is 0 nats.
  %% For symbolic regression MDL is a
  %% proxy for \# of continuous parameters.
}\vspace{-0.5cm}\label{baselineComparisons} \end{wraptable}

>>>>

Prior work on program learning has largely assumed a fixed, hand-engineered DSL,
both in classic symbolic program learning approaches (e.g., Metagol:~\cite{muggleton2015meta},
FlashFill:~\cite{gulwani2011automating}),
neural approaches  (e.g., RobustFill:~\cite{devlin2017robustfill}), and hybrids of neural and
symbolic methods (e.g., Neural-guided deductive search:~\cite{ngds}, DeepCoder:~\cite{balog2016deepcoder}).
A notable exception is the EC algorithm~\cite{Dechter:2013:BLV:2540128.2540316},
which also learns a library of subroutines.
We were motivated by EC, and go beyond it and other prior work through the following contributions:
(1) We show how to learn-to-learn programs in an expressive Lisp-like programming language;
(2) We give an algorithm for learning DSLs,
built on a formalism known as Fragment Grammars~\cite{tim};
and (3) We give a hierarchical Bayesian framing of
the problem that
allows a joint inference of the DSL and recognition model.

@@
